Probing the internal structure of quasars using microlensing events

### 2016-02-22 paper1/intro.tex
another set of corrections
a new ref

A whole range of models have been applied starting from simple geometric models to more complex, physically sensible models (\cite{2008Natur.455...78D}, \cite{2011ApJ...738...38B}, \cite{2009ApJ...706..497M}, \cite{2010ApJ...717.1092D}). 
A significant fraction of the later models predict a crescent shaped silhouette of the black hole. 
This motivated \cite{2013MNRAS.434..765K} to use a simple geometric crescent model to fit the data. 
The succesful results encouraged the authors to speculate that the shadow of the black hole will be observed in the near future with the previously mentioned observation method. \\

@@

%Irshad - you can add here your paragraphs

>>>>

A whole range of models have been applied starting from simple geometric models to more complex, physically sensible models (\cite{2008Natur.455...78D}, \cite{2011ApJ...738...38B}, \cite{2009ApJ...706..497M}, \cite{2010ApJ...717.1092D}, \cite{2016arXiv160205527F}). 
A significant fraction of the later models predict a crescent shaped silhouette of the black hole. 
This motivated \cite{2013MNRAS.434..765K} to use a simple geometric crescent model to fit the data. 
The succesful results encouraged the authors to speculate that the shadow of the black hole will be observed in the near future with the previously mentioned observation method. \\

@@
